\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\usepackage[scale=0.75]{geometry}
% personal data
\name{Popikov}{Andrey}
\title{Software Engineer}                               % optional, remove / comment the line if not wanted
\address{Voronezh}{Russia}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+7~(960)~103~20~74}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{agpopikov@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{agpopikov.info}                         % optional, remove / comment the line if not wanted
\social[github]{agpopikov}                              % optional, remove / comment the line if not wanted
\social[skype]{andrejpopikov}                               % optional, remove / comment the line if not wanted
\social[linkedin]{agpopikov}                               % optional, remove / comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2012--2016}{Computer Science Faculty}{Voronezh State University}{Voronezh}{\textit{Bachelor}}
{Department of "Programming and information technologies"}

\renewcommand{\listitemsymbol}{-~}

\section{Skills}
\cvitem{}{
\begin{itemize}
\item Good knowledge of basic algorithms \& network fundamentals.
\item Knowledge of Java (core, collections, concurrency) \& Kotlin language.
\item Experience in developing large projects with frameworks like Spring (Boot, Security, Web), Hibernate.
\item Good knowledge of Angular web-framework \& all modern web-apps ecosystem (NPM / Yarn, TypeScript, Sass).
\item Experience in working with infrastructure tools: Gradle, Docker, TestContainers, Ansible, CI (TeamCity, GitLab CI), Nginx.
\item Basic experience in applied cryptography (Java Cryptography Extension, smartcards apps, digital signatures).
\end{itemize}}


\section{Experience}
\cventry{2015--2019}{Lead Software Engineer}{Inleksys}{Voronezh}{}{
\begin{itemize}
\item Development team management (about 10 developers in team).
\item Developing web-applications using technologies like Java, Kotlin, Spring, PostgreSQL, Redis, Kafka, TypeScript, Angular.
\item Participating in optimizing CI processes \& new technologies adoption in this area.
\item Organizing internal lectures about Kotlin, PostgreSQL, modern CI practices. 
\item Developing different proof-of-concepts as a part of presale activities (including IoT projects \& mobile apps on Flutter platform).
\item Active participation in company HR-processess:
  \begin{itemize}
    \item Technical interviewing, working on materials and methodology improvement.
    \item Organizing Java \& Web development courses for students of our local schools.
  \end{itemize}
\end{itemize}}

\cventry{2014--2015}{Java Developer}{Vistar}{Voronezh}{}{
\begin{itemize}
\item Developing web-services with Java, Spring, MyBatis.
\item Developing prototypes of mobile applications on Apache Cordova platform.
\end{itemize}}

\cventry{2014--2015}{Intern}{Likeonyx}{Voronezh}{}{
\begin{itemize}
\item Participating in development projects on .Net (C\#, WPF) \& Ruby.
\end{itemize}}

\pagebreak

\section{Additional projects}
\cvlistitem{http://madtest.ru/ - modern quiz SaaS for news \& media services (now in final stage of development, preparing for launch).}{}
\cvlistitem{https://github.com/agpopikov/hob - Implementation of new version of Apple HomeKit Accessory Protocol over Bluetooth LE for embedded devices (work in progress).}

\section{Languages}
\cvitem{Russian}{Native}
\cvitem{English}{Intermediate}
\cvitem{German}{Beginner}

\section{Interests}
\cvlistitem{IoT devices engineering based on STM32 \& ESP32 chips, making first steps in FPGA programming (Xilinx Zynq family).}
\cvlistitem{Learning computational mathematics (especially computational fluid dynamics, FEM application, etc).}

\end{document}
